---
title: "Natural Hazards Risk Analysis Technical Working Group"
author : Md. Zia Uddin Foisal
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
logo : www/REACH.png
runtype : shiny
---
<script>
$('.navbar-logo').wrap('www/REACH.png');
</script>

```{r setup, include=FALSE}
library(flexdashboard)
```

Hydro-Meteorological Data - REACH{data-navmenu="Hydro-Meteorological Data"}
============================================================================== 
Row
-----------------------------------------------------------------------   
### Product Descriptions
```{r}

```

Pluvial Flooding Model – ARUP with IOM & REACH {data-navmenu="Flood Model"}
=======================================================================   
Column {data-width=650}
-----------------------------------------------------------------------
### Model Descriptions
```{r}

```
Column {data-width=350}
-----------------------------------------------------------------------
### Hydronamic Flood Model
```{r}

```

Flood Vulnerability Analysis – Deltares with WFP {data-navmenu="Flood Model"}
=======================================================================   
Column {data-width=350}
-----------------------------------------------------------------------
### Model Descriptions
```{r}

```
Column {data-width=650}
-----------------------------------------------------------------------
### Hydronamic Flood Model
```{r}

```


Flood Water Extent - REACH{data-orientation=rows data-navmenu="Flood Model"}
============================================================================== 
Row {data-width=650}
-----------------------------------------------------------------------   
### Chart A
```{r}

```
Row {data-width=350}
-----------------------------------------------------------------------
### Chart B
```{r}

```

Flood Water Volume - REACH {data-navmenu="Flood Model"}
============================================================================== 
Row {data-width=650}
-----------------------------------------------------------------------   
### Chart A
```{r}

```
Row {data-width=350}
-----------------------------------------------------------------------
### Chart B
```{r}

```


Structures Exposed to Flood - REACH{data-navmenu="Flood Model"}
============================================================================== 
Row {data-width=650}
-----------------------------------------------------------------------   
### Chart A
```{r}

```
Row {data-width=350}
-----------------------------------------------------------------------
### Chart B
```{r}

```

Area Exposed to Flood - REACH {data-navmenu="Flood Model"}
============================================================================== 
Row {data-width=650}
-----------------------------------------------------------------------   
### Chart A 
```{r}

```
Row {data-width=350}
-----------------------------------------------------------------------
### Chart B
```{r}

```



Landslide Susceptibility and Warning Model - COMPASS {data-navmenu="Landslide Model"}
============================================================================== 
Row {data-width=650}
-----------------------------------------------------------------------   
### Chart A
```{r}

```
Row {data-width=350}
-----------------------------------------------------------------------
### Chart D
```{r}

```


Wind Assessment - REACH with UNDP {data-navmenu="Wind Assessment"}
============================================================================== 
Row {data-width=350}
-----------------------------------------------------------------------   
### Chart C 
```{r}

```
Row {data-width=650}
-----------------------------------------------------------------------
### Chart B
```{r}

```
Storm Surge Analysis - REACH with IOM and UNHCR {data-navmenu="Storm Surge Analysis"}
============================================================================== 
Row {data-width=350}
-----------------------------------------------------------------------   
### Product Descriptions
```{r}

```
Row {data-width=650}
-----------------------------------------------------------------------
### Storm Surge Analysis
```{r}

```

Fire Risk Assessment - REACH {data-navmenu="Fire Risk Assessment"}
============================================================================== 
Row {data-width=350}
-----------------------------------------------------------------------   
### Product Descriptions
```{r}

```
Row {data-width=650}
-----------------------------------------------------------------------
### Storm Surge Analysis
```{r}

```





